Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex
results

As a comparison measure, we used the performance of the classifiers on predicting the cognitive state that the subject was in. Table~\ref{tab:results} illustrates the final results. Rows indicate various feature selection methods. The letter \emph{M} means Columns depict the used classifiers. For the classifiers depicted with (*), we used different structure for the data that we fit to them (take example from section where the selection is introduced).

@@

\begin{table*}[htdp]
\centering
{\small
\begin{tabular}{c|c|c|c|c}
& \textbf{Naive Bayes} & \textbf{Linear SVC} & \textbf{Naive Bayes*} & \textbf{Multivariate*} \\ \hline
PCA & 61.5 \% &  - & - & - \\
M-ROIs & 70.2 \% & 72.5 \% & 74.8 \% & 76.7 \% \\
Norm-M-ROIs & 71.7 \% & 71.3 \% & 75.8 \% & 77.1 \% \\
Norm-M-SD-ROIs & 65.6 \% & 69.8 \% & 69.4 \% & 65.0 \%\\
Norm/Vox-M-ROIs & 73.1 \% & 76.7 \% & 76.9 \% & 79.6 \% \\
\end{tabular}}
\caption{Performance results of three classifiers using different methods for feature selection and structure.}
\label{tab:results}
\end{table*}

>>>>

As a comparison measure, we used the performance of the classifiers on predicting the cognitive state that the subject was in. Table~\ref{tab:results} illustrates the overall performance of . Rows indicate various feature selection methods. The letter \emph{M} means Columns depict the used classifiers. For the classifiers depicted with (*), we used different structure for the data that we fit to them (take example from section where the selection is introduced).

@@

\begin{table*}[htdp]
\centering
{\small
\begin{tabular}{c|c|c|c|c}
& \textbf{Naive Bayes} & \textbf{Linear SVC} & \textbf{Naive Bayes*} & \textbf{Multivariate*} \\ \hline
PCA & 61.46 &  - & - & - \\
M-ROIs & 70.21 & 72.5 & 74.79 & 76.67 \\
Norm-M-ROIs & 71.67 & 71.25 & 75.83 & 77.08 \\
Norm-M-SD-ROIs & 65.63 & 69.79 & 69.38 & 65.0 \\
Norm/Vox-M-ROIs & 73.13 & 76.67 & 76.88 & 79.58 \\
\end{tabular}}
\caption{Performance results (in \%) of the three classifiers for different methods for feature selection and structure.}
\label{tab:results}
\end{table*}
